Community-Conditioned Language Models

### 2021-06-09 paper/paper.tex
note on n-gram models
remove plot_macros (and also lmodern ... why did we load that??)
conll is using the emnlp template
edit discussion

% Remove the "review" option to generate the final version.
\usepackage[review]{acl}

% Standard package includes
\usepackage{times}
\usepackage{latexsym}
\usepackage{newunicodechar}

@@

\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{siunitx}
\usepackage{booktabs}
\usepackage{pgfplots}
\usepackage{todonotes}
\usepackage{enumitem}
\usepackage{cleveref}
\usepackage{array}
\usepackage{makecell}
\usepackage{multirow}

\usepgfplotslibrary{groupplots}
\usepgfplotslibrary{statistics}
\pgfplotsset{compat=1.16}
\pgfplotsset{every tick label/.append style={font=\footnotesize}}

@@

\input{plot_macros}

@@

\begin{table}
  \small
  \centering
  \input{floats/model_results.tex}
  \caption{
    Performance of baseline (first row for each encoder architecture)
    and CCLM models.  The scope of perplexity and information gain
    ($M$) is the entire test set, i.e. $5000×510$ messages; \num{5000}
    for each community.}
  \label{tab:model-results}
\end{table}

We also consider performance stratified by community; that is,
$\Ppl_{M_j}$ and $\IG_{M_j}$, 
where $M_j$ is the set of messages originating from community $c_j$ 
(\cref{fig:comm-stratified-box}).
We observe a lot of variation in baseline perplexity
across communities, with $\Ppl_{M_j}$ ranging from \num{3.67} to
\num{93.58} for the best conditional LSTM model. %TODO make long table
While the absolute performance ($\Ppl_{M_j}$) of the LSTM models is better,
the best transformer models have somewhat higher information gain
than their LSTM counterparts.

\newcommand{\modelboxplot}[3]{
  \addplot+[
    boxplot={draw position=#3, box extend=0.3}, 
    draw=#2, mark=*, mark options={fill=#2, scale=0.5}, solid, fill=#2!10,
    area legend] 
    table [y=#1] {floats/comm.csv};
}
\begin{figure}[t]
\begin{tikzpicture}
  \begin{axis}[name=ig,
    height=7cm,width=8cm,
    boxplot/draw direction=x, axis x line*=bottom, axis y line*=left,y axis line style={opacity=0},
    xmax=1.6,
    ylabel=$l_c$, xlabel=$\IG_{M_j}$,
    legend style={font=\tiny,at={(1,1)},anchor=north east}, legend columns=2
    ]
    \addplot[thin, red, samples=2] coordinates {(1,-0.5)(1,3.5)};
    \foreach \lc in {0, ..., 3}{
      \modelboxplot{lstm-3-\lc_ig}{violet}{\lc+0.2}
      \modelboxplot{transformer-3-\lc_ig}{teal}{\lc-0.2}
    \legend{,LSTM, Transformer}
    }
  \end{axis}
  \begin{axis}[name=ppl,
    anchor=north west,at={($(ig.south west)-(0,1.1cm)$)},
    width=8cm, height=2.5cm, 
    boxplot/draw direction=x, axis x line*=bottom, hide y axis,
    xlabel=$\Ppl_{M_j}$,
    ]
    \modelboxplot{lstm-3_ppl}{violet}{0.2}
    \modelboxplot{transformer-3_ppl}{teal}{-.2}
  \end{axis}
\end{tikzpicture}
\caption{
  Average model performance by community.
  The boxes indicate upper and lower quartiles, while the whiskers are placed at the upper and lower maximum, with communities more than $1.5\times IQR$ (inter-quartile range) above the upper quartile considered outliers (represented as dots). The three most extreme outliers are excluded from this view (see \cref{fig:ppl-info-gain}).
   See also table 1 in the supplementary materials
   for a tabular version of these results with community names.
}
\label{fig:comm-stratified-box}
\end{figure}

@@

\begin{figure}
\begin{tikzpicture}
\begin{axis}[%
    axis x line*=bottom, axis y line*=left,
    xlabel=$\Ppl_{M_j}$, ylabel=$\IG_{M_j}$,
    width=7cm,
  ]
  \addplot+[%
    only marks,
    mark=*,
    mark options={scale=0.35, solid, color=violet!80, fill=violet},
    font=\tiny,
  ] table [x={lstm-3_ppl}, y={lstm-3-3_ig}] {floats/comm.csv};
\end{axis}
\end{tikzpicture}
\caption{
  Average community perplexity (x-axis) versus information gain (y-axis)
  for the best LSTM model ($l_c = 1$). Pearson's r=$-0.61$ (p<0.001).
}
\label{fig:ppl-info-gain}
\end{figure}

@@

Indiscernibility of a given community is a robust measure: it is
almost perfectly correlated across CCLMs (such as transformers, LSTM
and various values of $l_c$).  In fact, we observe a correlation
between the indiscernibility measures by every pair of models with
Pearson's $r \geq 0.96$ and $Bp < 0.0001$.

However, we observe that community-wise perplexity is only weakly (if at all) 
correlated with community indiscernibility under the corresponding latent 
LMCC (see \cref{tab:ind-corrs} and, for example, \cref{fig:cclm-lmcc-ppl}).
In other words, the linguistic complexity of a given community
is a poor predictor of how distinctive its language is.
%
\begin{table}
  \small
  \centering
  \begin{tabular}{llrrrr}
  \toprule
      & $l_c$ & $\Ppl_{M_j}$ & $\IG_{M_j}$ \\
  \midrule
  \multirow{4}{*}{LSTM}         & 0 &            - &             - \\
                                & 1 &         0.19 &         -0.40 \\
                                & 2 &         0.19 &         -0.43 \\
                                & 3 &         0.06 &         -0.45 \\
  \midrule
  \multirow{4}{*}{Transformer}  & 0 &         0.19 &         -0.41 \\
                                & 1 &         0.23 &         -0.43 \\
                                & 2 &         0.16 &         -0.39 \\
                                & 3 &         0.12 &         -0.40 \\
  \bottomrule
  \end{tabular}
  \caption{ (TODO: missing data) Pearson's $r$ correlation coefficient between community
    indiscernibility ($\Ind_j$) and two different predictors: CCLM
    perplexity on messages from community $c_j$ ($\Ppl_{M_j}$), and
    CCLM information gain on messages from $c_j$ ($\IG_{M_j}$). $p < 0.001$
    for all correlations except $\Ppl_{M_j}$ for the LSTM with 
  $l_c=3$ ($p=0.218$) and Transfomer with $l_c=3$ ($p=0.010$).}
  \label{tab:ind-corrs}
\end{table}

\begin{figure*}
  \begin{tikzpicture}
  \begin{groupplot}[
    group style={group size=2 by 1},
    legend style={anchor=north, legend columns=1, font=\tiny},
    every node near coord/.append style={font=\sffamily\tiny},%
    axis x line*=bottom, axis y line*=left,
  ]
  \nextgroupplot[xlabel=$\Ppl_{M_j}$, ylabel=$\Ind_j$]
      \addplot+[%
        only marks,
        mark=*,
        mark options={scale=0.35, solid, color=violet!80, fill=violet},
        font=\tiny,
      ] table [x={lstm-3-1_ppl}, y={lstm-3-1_indisc}] {floats/comm.csv};
  \nextgroupplot[xlabel=$\IG_{M_j}$, ylabel=$\Ind_j$, xmax=1.6]
      \addplot+[%
        only marks,
        mark=*,
        mark options={scale=0.35, solid, color=violet!80, fill=violet},
        font=\tiny,
      ] table [x={lstm-3-1_ig}, y={lstm-3-1_indisc}] {floats/comm.csv};
  \end{groupplot}
  \end{tikzpicture}
  \caption{%
    Community indiscernibility (y-axis), 
    in relationship to linguistic complexity (left) and 
    CCLM information gain (right). Shown here for the LSTM
    model with $l_c=1$. See \cref{tab:ind-corrs} for 
    Pearson's r correlations for all models.
    (Communities with \(\IG > 1.6\) (3 outliers) are hidden to make the correlation easier to observe.)
  }
  \label{fig:cclm-lmcc-ppl}
\end{figure*}

@@

On the other hand, community indiscernibility is correlated with
the information gain of the CCLM
on messages from that community's test set
(see \cref{tab:ind-corrs} and, for example, \cref{fig:cclm-lmcc-ppl}).
Communities for which the language model benefits most from 
the conditioned model are generally easier for the LMCC to classify.

Finally, we note that, even though community-conditioning affects
perplexity very little overall, it provides large benefits in term of
the underlying Bayesian classifier. Indiscernibility is on average
TODO with a standard deviation of TODO. Roughly speaking, this means
that, while the linguistic variations does not allow our model to
pinpoint the originating community of a message, it can often
eliminate TODO (a percentatge?) of communities as possible locations
for it. Further more, the information gain provided by
community-conditioning is a good predictor of how specific the
community is.

@@

\jp{Conclusion: perplexity (linguistic complexity) is not correlated
  to how recognisable a community is. Presumably (in general) some very specific
  lexical items are characteristic of a community.}

  \section{Social Analysis of CCLM community embeddings (TODO: better title)}\label{sec:embedding-analysis}

@@

Thus if \(d(L,S)\) is below the mean by several standard deviations, we can safely
assume that there is statistically significant correlation between
\(L\) and \(S\).  This is the case: we observe a difference between 61 and 68 standard deviations
(\cref{tab:embedding-correlations}). Further, it is clear that the CCLM embedding
capture some of the same information as the social-network embeddings.
We also give a sense of \emph{how} the correlation is manifested by
analysis of the two principal components of correlation in the
linguistic embeddings, \(U_0\) and \(U_1\). To do so we plot the
projection of embeddings on along \(U_0\) and \(U_1\), together with
the corresponding singular values.\jp{TODO}

@@

%\begin{figure*}[t]
%\begin{tikzpicture}
  %\begin{groupplot}[
    %group style={group size=2 by 1},
    %yticklabels={,,}, xticklabels={,,},
    %legend style={anchor=north, legend columns=1, font=\sffamily\tiny},
  %]
    %\nextgroupplot
    %\commscatter{lstm-3-1_pca1}{lstm-3-1_pca2}
    %\nextgroupplot
    %\commscatter{transformer-3-3_pca1}{transformer-3-3_pca2}
    %\legend{General interest,Videogames,Technology,Sports,Female-focused,Other}
  %\end{groupplot}
%\end{tikzpicture}
%\caption{Plot of embeddings along the 2 principal dimensions of correlation between .... TODO of an LSTM (left, $c=1$) and transformer (right, $c=3$) model.
%Color correspond the 5-means clustering of .... TODO}
%\label{fig:comm-pca}
%\end{figure*}

@@

% \jp{I propose that most of the following analysis should be spread between the relevant sections, and only have a tiny summary here + future work.}
To sum up our findings, 
we observed that various communities exhibit widely varying levels of
linguistic complexity \ref{hyp:varying-complexity}, with perplexity
per-word ranging from less than 34 to more than 65 for the best model 
architecture.

With indiscernibility values evenly ranging over the whole possible
range (1 to 510), we find that CCLMs can be used to recognize certain
communities based on latent Bayesian classification
\ref{hyp:LMCC-works}, but not all.  We cannot rule out that generic
communities exhibit distinctive linguistic patterns, but none of our
CCLMs are able to discern them. In contrast, the distinctive patterns
of narrow-topic communities are just as recognizable by all our LSTM
and Transformer models.

@@

We find that the layer at which the community embedding is taken into
account in a CCLM influences its perplexity \ref{hyp:layer-effect},\jp{Delete this hypothesis?}
albeit weakly. For LSTM models, the perplexity per word, averaged over
messages from all communities, varies between \num{49.60} and \num{50.83}. (with \num{51.99} for the\jp{update numbers?}
unconditioned model) The perplexity per word is slightly higher for
$l_c=0$, and has very little difference between the other models, with
$l_c=3$ being the best.  For transformer models, it varies between 
\num{52.28} and \num{78.76}. Here perplexity per-word is clearly not a monotonous
function of $l_c$: the maximum is reached at $l_c=2$. We did not
expect non-monotonicity, and leave studying this effect to future
work.

The pattern of information gain by community is similar across
architectures.  Communities that benefit most from the conditioned
model behave that way for both the LSTM and transformer.  However,
there are some differences.  For example, the subreddit
\emph{relationships} has an information gain of \num{1.018} for the
best CCLM LSTM but only \num{0.998} for the best transformer model.
Why was the LSTM able to take advantage of the community information
for this community, where the transformer was not?  It would be
interesting to investigate these differences in future work, since it
could reveal differences in the kind of linguistic variation the
different model architectures capture.\jp{update?}

>>>>

% Remove the "review" option to generate the final version.
\usepackage[review]{emnlp2021}

% Standard package includes
\usepackage{times}
\usepackage{latexsym}

@@

\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{siunitx}
\usepackage{booktabs}
\usepackage{todonotes}
\usepackage{enumitem}
\usepackage{cleveref}
\usepackage{array}
\usepackage{makecell}
\usepackage{multirow}

\usepackage{newunicodechar}

\usepackage{pgfplots}
\usepgfplotslibrary{groupplots}
\usepgfplotslibrary{statistics}
\pgfplotsset{compat=1.16}
\pgfplotsset{every tick label/.append style={font=\footnotesize}}

@@

@@

\begin{table}
  \small
  \centering
  \begin{tabular}{llrrr}
  \toprule
                                 &       & \makecell{test \\ epoch} & $\Ppl_M$ & $\IG_M$     \\
                                 & $l_c$ &         &                 &                   \\
  \midrule
  \multirow{5}{*}{LSTM}         & - &          12 &  68.74          &       -           \\
                                & 0 &          13 &  66.16          &    1.039          \\
                                & 1 &           7 &  \textbf{66.01} &    \textbf{1.041} \\
                                & 2 &           4 &  66.19          &    1.039          \\
                                & 3 &           4 &  66.35          &    1.036          \\
  \midrule
  \multirow{5}{*}{Transformer}  & - &           4 &  79.13          &        -          \\
                                & 0 &           4 &  \textbf{75.66} &    \textbf{1.046} \\
                                & 1 &           4 &  82.12          &    0.964          \\
                                & 2 &           7 &  83.53          &    0.947          \\
                                & 3 &           3 &  75.90          &    1.043          \\
  \bottomrule
  \end{tabular}
  \caption{
    Performance of baseline (first row for each encoder architecture)
    and CCLM models.  The scope of perplexity and information gain
    ($M$) is the entire test set, i.e. $5000×510$ messages; \num{5000}
    for each community.}
  \label{tab:model-results}
\end{table}

We also consider performance stratified by community; that is,
$\Ppl_{M_j}$ and $\IG_{M_j}$, 
where $M_j$ is the set of messages originating from community $c_j$ 
(\cref{fig:comm-stratified-box}).
We observe a lot of variation in baseline perplexity
across communities, with $\Ppl_{M_j}$ ranging from \num{3.67} to
\num{93.58} for the best conditional LSTM model 
(see supplementary materials for perplexity by community). %TODO keep? 
While the absolute performance ($\Ppl_{M_j}$) of the LSTM models is better,
the best transformer models have somewhat higher information gain
than their LSTM counterparts.

\newcommand{\modelboxplot}[3]{
  \addplot+[
    boxplot={draw position=#3, box extend=0.3}, 
    draw=#2, mark=*, mark options={fill=#2, scale=0.5}, solid, fill=#2!10,
    area legend] 
    table [y=#1] {floats/comm.csv};
}
\begin{figure}[t]
\begin{tikzpicture}
  \begin{axis}[name=ig,
    height=7cm,width=8cm,
    boxplot/draw direction=x, axis x line*=bottom, axis y line*=left,y axis line style={opacity=0},
    xmax=1.6,
    ylabel=$l_c$, xlabel=$\IG_{M_j}$,
    legend style={font=\tiny,at={(1,1)},anchor=north east}, legend columns=2
    ]
    \addplot[thin, red, samples=2] coordinates {(1,-0.5)(1,3.5)};
    \foreach \lc in {0, ..., 3}{
      \modelboxplot{lstm-3-\lc-ig}{violet}{\lc+0.2}
      \modelboxplot{transformer-3-\lc-ig}{teal}{\lc-0.2}
    \legend{,LSTM, Transformer}
    }
  \end{axis}
  \begin{axis}[name=ppl,
    anchor=north west,at={($(ig.south west)-(0,1.1cm)$)},
    width=8cm, height=2.5cm, 
    boxplot/draw direction=x, axis x line*=bottom, hide y axis,
    xlabel=$\Ppl_{M_j}$,
    ]
    \modelboxplot{lstm-3-ppl}{violet}{0.2}
    \modelboxplot{transformer-3-ppl}{teal}{-.2}
  \end{axis}
\end{tikzpicture}
\caption{
  Average model performance by community.
  The boxes indicate upper and lower quartiles, while the whiskers are placed at the upper and lower maximum, with communities more than $1.5\times IQR$ (inter-quartile range) above the upper quartile considered outliers (represented as dots). The three most extreme outliers are excluded from this view (see \cref{fig:ppl-info-gain}).
   See also table 1 in the supplementary materials
   for a tabular version of these results with community names.
}
\label{fig:comm-stratified-box}
\end{figure}

@@

\begin{figure}
\begin{tikzpicture}
\begin{axis}[%
    axis x line*=bottom, axis y line*=left,
    xlabel=$\Ppl_{M_j}$, ylabel=$\IG_{M_j}$,
    width=7cm,
  ]
  \addplot+[%
    only marks,
    mark=*,
    mark options={scale=0.35, solid, color=violet!80, fill=violet},
    font=\tiny,
  ] table [x={lstm-3-ppl}, y={lstm-3-3-ig}] {floats/comm.csv};
\end{axis}
\end{tikzpicture}
\caption{
  Average community perplexity (x-axis) versus information gain (y-axis)
  for the best LSTM model ($l_c = 1$). Pearson's r=$-0.61$ (p<0.001).
}
\label{fig:ppl-info-gain}
\end{figure}

@@

Indiscernibility of a given community is a robust measure: it is
almost perfectly correlated across CCLMs (such as transformers, LSTMs
and various values of $l_c$).  In fact, we observe a correlation
between the indiscernibility measures by every pair of models with
Pearson's $r \geq 0.96$ and $p < 0.0001$.

However, we observe that community-wise perplexity is only weakly (if at all) 
correlated with community indiscernibility under the corresponding latent 
LMCC (see \cref{tab:ind-corrs} and, for example, \cref{fig:cclm-lmcc-ppl}).
In other words, the linguistic complexity of a given community
is a poor predictor of how distinctive its language is.
\jp{Conclusion: perplexity (linguistic complexity) is not correlated
  to how recognisable a community is. Presumably (in general) some very specific
  lexical items are characteristic of a community.}
%
\begin{table}
  \small
  \centering
  \begin{tabular}{llrrrr}
  \toprule
      & $l_c$ & $\Ppl_{M_j}$ & $\IG_{M_j}$ \\
  \midrule
  \multirow{4}{*}{LSTM}         & 0 &         0.21 &         -0.41 \\
                                & 1 &         0.19 &         -0.40 \\
                                & 2 &         0.19 &         -0.43 \\
                                & 3 &         0.06 &         -0.45 \\
  \midrule
  \multirow{4}{*}{Transformer}  & 0 &         0.19 &         -0.41 \\
                                & 1 &         0.23 &         -0.43 \\
                                & 2 &         0.16 &         -0.39 \\
                                & 3 &         0.12 &         -0.40 \\
  \bottomrule
  \end{tabular}
  \caption{ Pearson's $r$ correlation coefficient between community
    indiscernibility ($\Ind_j$) and two different predictors: CCLM
    perplexity on messages from community $c_j$ ($\Ppl_{M_j}$), and
    CCLM information gain on messages from $c_j$ ($\IG_{M_j}$). $p < 0.001$
    for all correlations except $\Ppl_{M_j}$ for the LSTM with 
  $l_c=3$ ($p=0.218$) and Transfomer with $l_c=3$ ($p=0.010$).}
  \label{tab:ind-corrs}
\end{table}

\begin{figure*}
  \begin{tikzpicture}
  \begin{groupplot}[
    group style={group size=2 by 1},
    legend style={anchor=north, legend columns=1, font=\tiny},
    every node near coord/.append style={font=\sffamily\tiny},%
    axis x line*=bottom, axis y line*=left,
  ]
  \nextgroupplot[xlabel=$\Ppl_{M_j}$, ylabel=$\Ind_j$]
      \addplot+[%
        only marks,
        mark=*,
        mark options={scale=0.35, solid, color=violet!80, fill=violet},
        font=\tiny,
      ] table [x={lstm-3-1-ppl}, y={lstm-3-1-indisc}] {floats/comm.csv};
  \nextgroupplot[xlabel=$\IG_{M_j}$, ylabel=$\Ind_j$, xmax=1.6]
      \addplot+[%
        only marks,
        mark=*,
        mark options={scale=0.35, solid, color=violet!80, fill=violet},
        font=\tiny,
      ] table [x={lstm-3-1-ig}, y={lstm-3-1-indisc}] {floats/comm.csv};
  \end{groupplot}
  \end{tikzpicture}
  \caption{%
    Community indiscernibility (y-axis), 
    in relationship to linguistic complexity (left) and 
    CCLM information gain (right). Shown here for the LSTM
    model with $l_c=1$. See \cref{tab:ind-corrs} for 
    Pearson's r correlations for all models.
    (Communities with \(\IG > 1.6\) (3 outliers) are hidden to make the correlation easier to observe.)
  }
  \label{fig:cclm-lmcc-ppl}
\end{figure*}

@@

On the other hand, community indiscernibility is correlated with
the information gain of the CCLM
on messages from that community's test set
(see \cref{tab:ind-corrs} and, for example, \cref{fig:cclm-lmcc-ppl}).
Communities for which the language model benefits most from 
the conditioned model are generally easier for the LMCC to classify.
Intuitively this makes sense:
the more distinctive a community's language is,
the easier it is to guess where messages from that community originated
and the easier it is to predict the content of the message if you know the community.

Finally, we note that, even though community conditioning affects
perplexity very little overall, it provides large benefits in term of
the underlying Bayesian classifier. Indiscernibility is on average
\num{0.57} with a standard deviation of \num{0.22}. Roughly speaking, this means
that, while the linguistic variations does not allow our model to
pinpoint the originating community of a message, it can often
eliminate TODO (a percentatge?) of communities as possible locations \bn{43\%?}
for it. Further more, the information gain provided by
community-conditioning is a good predictor of how specific the
community is.

@@

\section{Comparison of CCLM community embeddings with a social network embedding}\label{sec:embedding-analysis}

@@

Thus if \(d(L,S)\) is below the mean by several standard deviations, we can safely
assume that there is statistically significant correlation between
\(L\) and \(S\).  This is the case: we observe a difference between 61 and 68 standard deviations
(\cref{tab:embedding-correlations}). Further, it is clear that the CCLM embedding
capture some of the same information as the social-network embeddings.
We also give a sense of \emph{how} the correlation is manifested by
analysis of the two principal components of correlation in the
linguistic embeddings, \(U_0\) and \(U_1\). To do so we plot the
projection of each embedding along their first two principle components
which, together with the corresponding singular values, gives an idea
of how much and in what way they differ (see supplementary materials).

@@

%\begin{figure*}[t]
%\begin{tikzpicture}
  %\begin{groupplot}[
    %group style={group size=2 by 1},
    %yticklabels={,,}, xticklabels={,,},
    %legend style={anchor=north, legend columns=1, font=\sffamily\tiny},
  %]
    %\nextgroupplot
    %\commscatter{lstm-3-1-pca1}{lstm-3-1-pca2}
    %\nextgroupplot
    %\commscatter{transformer-3-3_pca1}{transformer-3-3_pca2}
    %\legend{General interest,Videogames,Technology,Sports,Female-focused,Other}
  %\end{groupplot}
%\end{tikzpicture}
%\caption{Plot of embeddings along the 2 principal dimensions of correlation between .... TODO of an LSTM (left, $c=1$) and transformer (right, $c=3$) model.
%Color correspond the 5-means clustering of .... TODO}
%\label{fig:comm-pca}
%\end{figure*}

@@

% \jp{I propose that most of the following analysis should be spread between the relevant sections, and only have a tiny summary here + future work.}
To sum up our findings, 
we observed that various communities exhibit widely varying levels of
linguistic complexity \ref{hyp:varying-complexity}. For the best model architecture,
perplexity per-word ranges from less than \num{4} to more than \num{93} 
(but with only 25\% of communities under 63).

With indiscernibility, values are distributed evenly over the whole possible
range (1 to 510). We find that CCLMs can be used to recognize certain
communities based on latent Bayesian classification
\ref{hyp:LMCC-works}, but not all.  In general, we observe that the least
discernible communities all have a very conversational, general-interest
premise. We cannot rule out that these more generic
communities exhibit distinctive linguistic patterns, but none of our
CCLMs are able to discern them. In contrast, the distinctive patterns
of narrow-topic communities are just as recognizable by all our LSTM
and Transformer models.

@@

We find that the layer at which the community embedding is taken into
account ($l_c$) has a weak effect on the perplexity of the CCLM
\ref{hyp:layer-effect}
For LSTM models, the perplexity per word, averaged over
messages from all communities, was between \num{66.01} and \num{66.35}
(with \num{68.74} for the unconditioned model).
For transformer models, it varies a bit more, between \num{75.66} and \num{83.53},
but this seems to be mainly due to the poor performance of the models where
the community embedding is inserted between transformer layers
($l_c=2$ and $3$ both test above the unconditioned transformer's 
average perplexity of \num{79.13}).
This could have something to do with the community embedding and linear layer
interrupting the delicate layer normalisation between transformer encoder layers.

The pattern of information gain by community is similar across
architectures.  Communities that benefit most from the conditioned
model behave that way for both the LSTM and transformer.  However,
there are some differences.  For example, many of the communities with the biggest 
difference in information gain between the $l_c=0$ and $l_c=3$ LSTMs 
seem to be organised around trading collectables or organising virtual meetups
(\emph{friendsafari},
\emph{Fireteams},
\emph{RandomActsOfGaming},
\emph{randomactsofcsgo},
\emph{Pokemongiveaway},
\emph{ACTrade},
\emph{SVExchange})
Why was the model where the community information was incorporated before
the LSTM able to take better advantage of it for these communities in particular? 
It would be interesting to investigate these differences in future work, since it
could reveal differences in the kind of linguistic variation the
different model architectures capture.
